### 2011-11-22 doc/theses/vitasek/appendix-b-iss.tex
Thesis: merging Kesy.

Subclass the \texttt{Abstract\-Experiment\-Set} class, override \texttt{get\-Name()} to provide the name of this set and finally override \texttt{get\-Experiments()} to return the list of~\texttt{Ex\-per\-i\-ment\-Parameters} that will constitute this sit.

>>>>

Subclass the \texttt{Abstract\-Experiment\-Set} class, override \texttt{get\-Name()} to provide the name of this set and finally override \texttt{get\-Experiments()} to return the list of~\texttt{Ex\-per\-i\-ment\-Parameters} that will constitute this set.
